% mainfile: ./cv.tex
\begin{itemize}
\item
  \ressubheading{Virginia Tech}{Arlington, VA}{GRA in Discovery Analytics 
      Center. Advised by Dr. Naren Ramakrishnan}{Fall 2011 - Current}\vspace{0.5em}
  \begin{itemize}
    \resitem{Worked on Disease Forecasting. Create streaming data ingestion module
      for Disease surveillance, Weather and News. 
      Implemented big-date disease forecasting pipeline for EMBERS in 
      \textit{python} over EMBERS \textit{AWS} cluster framework. 
      Forecasts sent in real-time without human supervision and continuously 
      evaluated}
    \resitem{Interfaced with several agencies such as IARPA and CDC for disease
      forecasting problems. Collaborated with several institutes such as
      \textit{NDSSL}, Virginia Tech, \textit{Healthmap}, Harvard Medical School
      and \textit{YeLab}, University of Michigan, Ann Arbor}
    \resitem{Helped organize and run flu forecasting market in collaboration with Scicast, 
      George Mason University}
    \resitem{Collaborated on several projects such as pattern detection in 
      Ionospheric Radiation, with ECE VT and solar Photo-voltaic energy prediction
      with HP Labs}
  \end{itemize}\vspace{0.5em}
\item
  \ressubheading{Microsoft Research India}{Bangalore, IN}{Visiting Researcher, 
  invited by Dr. Srivatsan Laxman}{June 2012}\vspace{0.5em}
  \begin{itemize}
    \resitem{Worked on formalization of histogram estimation using random
      resampling with possible applications towards distribution prediction under
      out-of-core data estimation problems}
  \end{itemize}\vspace{0.5em}
\item
  \ressubheading{Amazon Web Services}{Seattle, WA}{SDE Intern, 
      mentored by Paul Sharpe}{Summer 2011}\vspace{0.5em}
  \begin{itemize}
    \resitem{Worked on updating an Internal Console of AWS Beanstalk towards
      more real-time status monitoring of the same. Implemented in 
      \textit{java} using \textit{Spring-Hibernate} framework using
      a combination of \textit{JSP, js, css, and html5}}
  \end{itemize}\vspace{0.5em}
\item
  \ressubheading{Virginia Tech}{Blacksburg, VA}{GTA in Dept.\ of Computer 
      Science. Instructor: Mr. N.D. Barnette}{Fall 2010 - Spring 2011}\vspace{0.5em}
  \begin{itemize}
    \resitem{Grading and tutoring duties for C++ programming 
    class of $\approx$ 200 students.}
  \end{itemize}\vspace{0.5em}
\item
  \ressubheading{Indian Institute of Technology, Delhi}{Delhi, IN}{Research Intern, 
    advised by Prof. B.K. Panigrahi}{Summer 2009}\vspace{0.5em}
  \begin{itemize}
    \resitem{Worked on application of heuristic optimization and machine learning
    methods to power system characterization and early Epilepsy detection using
    wavelets. Published several papers to several journals and conferences.}
  \end{itemize}
\end{itemize}
